Chronic imaging of cortical oxygen tension and blood flow after targeted vascular occlusion

### 2018-04-26 article.tex
Eliminated unused custom commands
Added craniotomy location details to the animal methods section

% Define custom commands
\makeatletter
    \newcommand*\rfrac[2]{{}{#1}\!/{#2}}                    % Inline fraction with slash
    \newcommand{\pO}{\ensuremath{\text{pO}_2}} 	            % pO2 shortcut
    \newcommand{\rpm}{\raisebox{.2ex}{$\scriptstyle\pm$}}   % Raised plus/minus sign
    \newcolumntype{?}[1]{!{\vrule width #1}} 	            % Thick vertical line for table
\makeatother

@@

\subsection{Animal Preparation}
Mice (CD-1, male, 25-30 g, Charles River) were anesthetized with medical air vaporized isoflurane (2\%) via nose-cone inhalation. Body temperature was maintained at 37 $^\circ$C with a feedback heating pad (DC Temperature Controller, Future Health Concepts). Arterial oxygen saturation, heart rate, and breath rate were monitored via pulse oximetry (MouseOx, Starr Life Sciences). After induction, mice were placed supine in a stereotaxic frame (Narishige Scientific Instrument Lab) and administered carprofen (5 mg/kg, subcutaneous) and dexamethasone (2 mg/kg, intramuscular) to reduce inflammation of the brain during the craniotomy procedure. The scalp was shaved and resected to expose skull between the bregma and lambda cranial coordinates. A thin layer of cyanoacrylate (Vetbond, 3M) was applied to the exposed skull to facilitate the adhesion of dental cement during a later step. A 3-4 mm diameter portion of the skull was removed with a dental drill (Ideal Microdrill, 0.8 mm burr, Fine Science Tools) under regular artificial cerebrospinal fluid perfusion. A 5-8 mm round cover glass (\#1.5, World Precision Instruments) was placed over the exposed brain with a layer of artificial cerebrospinal fluid between the two. While applying gentle pressure to the cover glass, a dental cement mixture was deposited along the perimeter, bonding it to the surrounding skull. This process created a sterile, air-tight seal around the craniotomy and allowed for restoration of intracranial pressure. A layer of cyanoacrylate was applied over the dental cement to further seal the cranial window. Animals were allowed to recover from anesthesia and monitored for cranial window integrity and normal behavior for two weeks prior to imaging. All imaging sessions were conducted using medical air with 1.5\% vaporized isoflurane. The Institutional Animal Care and Use Committee at The University of Texas at Austin approved of all experiments.

>>>>

% Define pO2 shortcut
\makeatletter
    \newcommand{\pO}{\ensuremath{\text{pO}_2}}
\makeatother

@@

\subsection{Animal Preparation}
Mice (CD-1, male, 25-30 g, Charles River) were anesthetized with medical air vaporized isoflurane (2\%) via nose-cone inhalation. Body temperature was maintained at 37 $^\circ$C with a feedback heating pad (DC Temperature Controller, Future Health Concepts). Arterial oxygen saturation, heart rate, and breath rate were monitored via pulse oximetry (MouseOx, Starr Life Sciences). After induction, mice were placed supine in a stereotaxic frame (Narishige Scientific Instrument Lab) and administered carprofen (5 mg/kg, subcutaneous) and dexamethasone (2 mg/kg, intramuscular) to reduce inflammation of the brain during the craniotomy procedure. The scalp was shaved and resected to expose skull between the bregma and lambda cranial coordinates. A thin layer of cyanoacrylate (Vetbond Tissue Adhesive, 3M) was applied to the exposed skull to facilitate the adhesion of dental cement during a later step. A 3 mm diameter portion of the skull over the frontoparietal cortex was removed with a dental drill (Ideal Microdrill, 0.8 mm burr, Fine Science Tools) while leaving the dura intact. The craniotomy was performed under regular perfusion of artificial cerebrospinal fluid to protect the brain from overheating. A 5 mm round cover glass (\#1.5, World Precision Instruments) was placed over the exposed brain with a layer of artificial cerebrospinal fluid between the two. While applying gentle pressure to the cover glass, a dental cement mixture was deposited along the perimeter, bonding it to the surrounding skull. This process created a sterile, air-tight seal around the craniotomy and allowed for restoration of intracranial pressure. A layer of cyanoacrylate was applied over the dental cement to further seal the cranial window. The medial and anterior edges of the window were approximately 2 mm rostral to bregma and 0.5 mm lateral to midline. Animals were allowed to recover from anesthesia and monitored for cranial window integrity and normal behavior for two weeks prior to imaging. All imaging sessions were conducted using medical air with 1.5\% vaporized isoflurane. The Institutional Animal Care and Use Committee at The University of Texas at Austin approved of all experiments.
